The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-20 document/ms.tex
paramtab format
table format
formatting of acknowledgements

% \usepackage{endnotes}
% \let\footnote=\endnote

@@

\begin{floattable}
\begin{deluxetable}{cccccccccl}
\tabletypesize{\footnotesize}
\caption{The inferred parameters for the long-period transiting exoplanet
candidates \label{tab:catalog}}
\include{paramtab}
\tablenotetext{*}{The equilibrium temperature is computed assuming zero
albedo.}
\tablenotetext{\dagger}{Candidate has two observed transits.}
\tablenotetext{a}{Included in the \citet{Wang:2015} catalog.}
\tablenotetext{b}{Included in the \citet{Uehara:2016} catalog.}
\tablecomments{The values and uncertainties indicate the 16-th, 50-th, and
84-th percentiles of the posterior samples for each parameter.}
\end{deluxetable}
\end{floattable}

@@

TDM was supported by the National Aeronautics and Space
Administration, under the \kepler\ participating
scientist program (grant NNX14AE11G), and is grateful for the
hospitality of both the Institute for Advanced Study and Carnegie
Observatories that helped support this work.

DWH was partially supported by the National Science Foundation (grant
IIS-1124794), the National Aeronautics and Space Administration (grant
NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
E.A. acknowledges support from NASA grants NNX13AF20G, NNX13AF62G, and NASA
Astrobiology Institutes Virtual Planetary Laboratory, supported by NASA under
cooperative agreement NNH05ZDA001C.

@@

\newpage
\bibliography{peerless}

% \theendnotes

>>>>

@@

\begin{floattable}
\begin{deluxetable}{cccccccccccl}
\tabletypesize{\scriptsize}
\caption{The inferred parameters for the long-period transiting exoplanet
candidates \label{tab:catalog}}
\include{paramtab}
\tablenotetext{*}{The equilibrium temperature is computed assuming zero
albedo.}
\tablenotetext{\dagger}{The KOI number and, if applicable, the \kepler\ number
for the target.}
\tablenotetext{a}{Included in the \citet{Wang:2015} catalog.}
\tablenotetext{b}{Included in the \citet{Uehara:2016} catalog.}
\tablenotetext{c}{Candidate has two observed transits.}
\tablecomments{The values and uncertainties indicate the 16-th, 50-th, and
84-th percentiles of the posterior samples for each parameter.}
\end{deluxetable}
\end{floattable}

@@

T.D.M.\ was supported by the National Aeronautics and Space
Administration, under the \kepler\ participating
scientist program (grant NNX14AE11G), and is grateful for the
hospitality of both the Institute for Advanced Study and Carnegie
Observatories that helped support this work.
D.W.H.\ was partially supported by the National Science Foundation (grant
IIS-1124794), the National Aeronautics and Space Administration (grant
NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
E.A.\ acknowledges support from NASA grants NNX13AF20G, NNX13AF62G, and NASA
Astrobiology Institutes Virtual Planetary Laboratory, supported by NASA under
cooperative agreement NNH05ZDA001C.

@@

\bibliography{peerless}
